---
title: "DSProject3"
output: html_document
date: "2024-04-02"
---

# libraries
```{r}
library(tidyverse)
library(opencv)
library(raster)
library(sp)
library(colorfindr)
library(keras)
library(tensorflow)
library(reticulate)
library (magick)
library(purrr)
library(gifski)
library(hues)
library(eyedroppeR)
```

# Load in the Kaggle Data
```{r}
typedf <- read.csv("~/Desktop/DS4002/Project3/pokemon.csv")
view(typedf)
```

# Clean the Data
```{r}
typedf2 <- typedf
typedf2$Type1 <- as.factor(typedf2$Type1) #make types factors
typedf2$Type2 <- as.factor(typedf2$Type2)

#typedf2$primtype <- typedf2$Type1

#levels(typedf2$primtype) = c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18) #

#summary(typedf2$primtype)
```

```{r}
#piplupcolors <- get_colors("Project3/images/piplup.png")

#piplupcolors 

#dim(readPNG("Project3/images/piplup.png"))
```

```{r}
#install_tensorflow(extra_packages="pillow")
#install_keras()
```

```{r}
#getwd()

#folder = "Project3/images/"

#setwd(folder)
#getwd()

#file.png <- list.files(folder, pattern ="*.png", ignore.case = TRUE, full.names = TRUE)

#list(file.png)
```





# Randomly generated 216 images (30% of data set) to serve as the testing set. 
```{r}
pokemon <- typedf2
#pokemon <- pokemon %>% mutate_all(na_if,"")
pokemon <- pokemon[1:721,]
list_space <- c("1 4 9 13 15 17 18 24 27 32 33 36 41 44 49 50 58 59 64 65 68 69 70 71 72 79 81 83 84 86 90 92 94 96 100 101 105 107 112 113 114 119 122 123 124 127 129 132 134 138 144 148 158 167 170 171 172 178 184 186 187 188 192 196 203 205 210 215 217 219 222 223 227 228 238 239 240 241 245 255 258 262 265 267 269 274 276 277 279 285 292 294 295 298 300 304 305 308 310 322 323 325 326 327 328 333 339 342 352 359 360 361 362 363 370 379 383 384 386 388 389 390 391 394 396 397 398 399 400 402 405 406 409 412 414 415 419 420 422 424 425 426 434 435 437 438 446 449 450 460 464 465 476 478 479 482 486 487 492 493 496 503 516 517 520 521 528 530 532 539 541 556 561 562 565 567 571 577 578 579 580 588 595 596 597 598 607 608 610 611 618 620 622 624 626 632 643 644 650 651 656 659 665 668 673 677 680 687 692 696 700 702 710 711 716 721")
numbers <- unlist(strsplit(list_space, " "))
integers <- as.integer(numbers)
pokemon_test <- pokemon[c(integers),]
#pokemon_test

```



# Created color palettes for each Pokemon type for EDA

Flying Primary Type
```{r}
folder = "Project3/flying"
setwd(folder)
getwd()

images.png <- list.files(folder, pattern ="*.png", ignore.case = TRUE, full.names = TRUE)
images.png

flyingcolors <- data.frame()

for (i in 1:length(images.png)){
    #print(i)
    filecolors <- get_colors(images.png[i], top_n = 3)
    flyingcolors <- rbind(flyingcolors, filecolors)
    #swatch(filecolors$col_hex)
}
swatch(flyingcolors$col_hex)
flyingcolors2 <- flyingcolors %>% group_by(col_hex) %>% summarize(tot_freq = sum(col_freq)) %>% arrange(desc(tot_freq)) %>% top_n(7) %>% mutate(type = "flying")
swatch(flyingcolors2$col_hex)
```

Fairy Primary Type 
```{r}
folder = "Project3/fairy"
setwd(folder)
getwd()

images.png <- list.files(folder, pattern ="*.png", ignore.case = TRUE, full.names = TRUE)
images.png 

fairycolors <- data.frame()

for (i in 1:(length(images.png))){ 
    filecolors <- get_colors(images.png[i], top_n = 3)
    fairycolors <- rbind(fairycolors, filecolors)
}
#swatch(fairycolors$col_hex) # total swatch of all colors
fairycolors2 <- fairycolors %>% group_by(col_hex) %>% summarize(tot_freq = sum(col_freq)) %>% arrange(desc(tot_freq)) %>% top_n(7) %>% mutate(type = "fairy")
swatch(fairycolors2$col_hex) #swatch of top 7 most popular colors

```

Ghost Primary Type
```{r}
folder = "Project3/ghost"
setwd(folder)
getwd()

images.png <- list.files(folder, pattern ="*.png", ignore.case = TRUE, full.names = TRUE)
images.png

ghostcolors <- data.frame()

for (i in 1:length(images.png)){
    filecolorsg <- get_colors(images.png[i], top_n = 3)
    ghostcolors <- rbind(ghostcolors, filecolorsg)
}
#swatch(ghostcolors$col_hex)
ghostcolors2 <- ghostcolors %>% group_by(col_hex) %>% summarize(tot_freq = sum(col_freq)) %>% arrange(desc(tot_freq)) %>% top_n(7) %>% mutate(type = "ghost")
swatch(ghostcolors2$col_hex)
```


Bug Primary Type
```{r}
folder = "Project3/bug"
setwd(folder)
getwd()

imagesbug.png <- list.files(folder, pattern ="*.png", ignore.case = TRUE, full.names = TRUE)
imagesbug.png

bugcolors <- data.frame()

for (i in 1:length(imagesbug.png)){
    filecolorsb <- get_colors(imagesbug.png[i], top_n = 3)
    bugcolors <- rbind(bugcolors, filecolorsb)
    #swatch(filecolors$col_hex)
}
bugcolors2 <- bugcolors %>% group_by(col_hex) %>% summarize(tot_freq = sum(col_freq)) %>% arrange(desc(tot_freq)) %>% top_n(7) %>% mutate(type = "bug")
swatch(bugcolors2$col_hex)
```

Dark Primary Type
```{r}
folder = "Project3/dark"
setwd(folder)
getwd()

imagesdark.png <- list.files(folder, pattern ="*.png", ignore.case = TRUE, full.names = TRUE)
imagesdark.png

darkcolors <- data.frame()

for (i in 1:length(imagesdark.png)){
    filecolorsd <- get_colors(imagesdark.png[i], top_n = 3)
    darkcolors <- rbind(darkcolors, filecolorsd)
}
darkcolors2 <- darkcolors %>% group_by(col_hex) %>% summarize(tot_freq = sum(col_freq)) %>% arrange(desc(tot_freq)) %>% top_n(7) %>% mutate(type = "dark")
swatch(darkcolors2$col_hex)
```

Dragon Primary Type
```{r}
folder = "Project3/dragon"
setwd(folder)
getwd()

imagesdragon.png <- list.files(folder, pattern ="*.png", ignore.case = TRUE, full.names = TRUE)
imagesdragon.png

dragoncolors <- data.frame()

for (i in 1:length(imagesdragon.png)){
    print(imagesdragon.png[i])
    filecolorsdr <- get_colors(imagesdragon.png[i], top_n = 3)
    dragoncolors <- rbind(dragoncolors, filecolorsdr)
}
dragoncolors2 <- dragoncolors %>% group_by(col_hex) %>% summarize(tot_freq = sum(col_freq)) %>% arrange(desc(tot_freq)) %>% top_n(7) %>% mutate(type = "dragon")
swatch(dragoncolors2$col_hex)
```

Electric Primary Type
```{r}
folder = "Project3/electric"
setwd(folder)
getwd()

imagesele.png <- list.files(folder, pattern ="*.png", ignore.case = TRUE, full.names = TRUE)
imagesele.png

electriccolors <- data.frame()

for (i in 1:length(imagesele.png)){
    filecolorsele <- get_colors(imagesele.png[i], top_n = 3)
    electriccolors <- rbind(electriccolors, filecolorsele)
}
#swatch(electriccolors$col_hex)
electriccolors2 <- electriccolors %>% group_by(col_hex) %>% summarize(tot_freq = sum(col_freq)) %>% arrange(desc(tot_freq)) %>% top_n(7) %>% mutate(type = "electric")
swatch(electriccolors2$col_hex)
```


Fighting Primary Type
```{r}
folder = "Project3/fighting"
setwd(folder)
getwd()

imagesfighting.png <- list.files(folder, pattern ="*.png", ignore.case = TRUE, full.names = TRUE)
imagesfighting.png

fightingcolors <- data.frame()

for (i in 1:length(imagesfighting.png)){
    filecolorsfighting <- get_colors(imagesfighting.png[i], top_n = 3)
    fightingcolors <- rbind(fightingcolors, filecolorsfighting)
}
fightingcolors2 <- fightingcolors %>% group_by(col_hex) %>% summarize(tot_freq = sum(col_freq)) %>% arrange(desc(tot_freq)) %>% top_n(7) %>% mutate(type = "fighting")
swatch(fightingcolors2$col_hex)
```

Fire Primary Type
```{r}
folder = "Project3/fire"
setwd(folder)
getwd()

imagesfire.png <- list.files(folder, pattern ="*.png", ignore.case = TRUE, full.names = TRUE)
imagesfire.png

firecolors <- data.frame()

for (i in 1:length(imagesfire.png)){
    filecolorsfire <- get_colors(imagesfire.png[i], top_n = 3)
    firecolors <- rbind(firecolors, filecolorsfire)
    #swatch(filecolors$col_hex)
}
firecolors2 <- firecolors %>% group_by(col_hex) %>% summarize(tot_freq = sum(col_freq)) %>% arrange(desc(tot_freq)) %>% top_n(7) %>% mutate(type = "fire")
swatch(firecolors2$col_hex)
```

Grass Primary Type
```{r}
folder = "Project3/grass"
setwd(folder)
getwd()

imagesgrass.png <- list.files(folder, pattern ="*.png", ignore.case = TRUE, full.names = TRUE)
imagesgrass.png

grasscolors <- data.frame()

for (i in 1:length(imagesgrass.png)){
    filecolorsgrass <- get_colors(imagesgrass.png[i], top_n = 3)
    grasscolors <- rbind(grasscolors, filecolorsgrass)
}
grasscolors2 <- grasscolors %>% group_by(col_hex) %>% summarize(tot_freq = sum(col_freq)) %>% arrange(desc(tot_freq)) %>% top_n(7) %>% mutate(type = "grass")
swatch(grasscolors2$col_hex)
```

Ground Primary Type
```{r}
folder = "Project3/ground"
setwd(folder)
getwd()

imagesgr.png <- list.files(folder, pattern ="*.png", ignore.case = TRUE, full.names = TRUE)
imagesgr.png

groundcolors <- data.frame()

for (i in 1:length(imagesgr.png)){
    #print(imagesgr.png[i])
    filecolorsgr <- get_colors(imagesgr.png[i], top_n = 3)
    groundcolors <- rbind(groundcolors, filecolorsgr)
    #swatch(filecolors$col_hex)
}
groundcolors2 <- groundcolors %>% group_by(col_hex) %>% summarize(tot_freq = sum(col_freq)) %>% arrange(desc(tot_freq)) %>% top_n(7) %>% mutate(type = "ground")
swatch(groundcolors2$col_hex)
```

Ice Primary Type
```{r}
folder = "Project3/ice"
setwd(folder)
getwd()

imagesice.png <- list.files(folder, pattern ="*.png", ignore.case = TRUE, full.names = TRUE)
imagesice.png

icecolors <- data.frame()

for (i in 1:length(imagesice.png)){
    print(imagesice.png[i])
    filecolorsice <- get_colors(imagesice.png[i], top_n = 3)
    icecolors <- rbind(icecolors, filecolorsice)
    #swatch(filecolors$col_hex)
}
icecolors2 <- icecolors %>% group_by(col_hex) %>% summarize(tot_freq = sum(col_freq)) %>% arrange(desc(tot_freq)) %>% top_n(7) %>% mutate(type = "ice")
swatch(icecolors2$col_hex)
```


Normal Primary Type
```{r}
folder = "Project3/normal"
setwd(folder)
getwd()

imagesnormal.png <- list.files(folder, pattern ="*.png", ignore.case = TRUE, full.names = TRUE)
imagesnormal.png

normalcolors <- data.frame()

for (i in 1:length(imagesnormal.png)){
    filecolorsnormal <- get_colors(imagesnormal.png[i], top_n = 3)
    normalcolors <- rbind(normalcolors, filecolorsnormal)
}
normalcolors2 <- normalcolors %>% group_by(col_hex) %>% summarize(tot_freq = sum(col_freq)) %>% arrange(desc(tot_freq)) %>% top_n(7) %>% mutate(type = "normal")
swatch(normalcolors2$col_hex)
```

Poison Primary Type
```{r}
folder = "Project3/poison"
setwd(folder)
getwd()

imagespoison.png <- list.files(folder, pattern ="*.png", ignore.case = TRUE, full.names = TRUE)
imagespoison.png

poisoncolors <- data.frame()

for (i in 1:length(imagespoison.png)){
    filecolorspoison <- get_colors(imagespoison.png[i], top_n = 3)
    poisoncolors <- rbind(poisoncolors, filecolorspoison)
}
poisoncolors2 <- poisoncolors %>% group_by(col_hex) %>% summarize(tot_freq = sum(col_freq)) %>% arrange(desc(tot_freq)) %>% top_n(7) %>% mutate(type = "poison")
swatch(poisoncolors2$col_hex)
```

Psychic Primary Type
```{r}
folder = "Project3/psychic"
setwd(folder)
getwd()

imagespsychic.png <- list.files(folder, pattern ="*.png", ignore.case = TRUE, full.names = TRUE)
imagespsychic.png

psychiccolors <- data.frame()

for (i in 1:length(imagespsychic.png)){
    filecolorspsychic <- get_colors(imagespsychic.png[i], top_n = 3)
    psychiccolors <- rbind(psychiccolors, filecolorspsychic)
}
psychiccolors2 <- psychiccolors %>% group_by(col_hex) %>% summarize(tot_freq = sum(col_freq)) %>% arrange(desc(tot_freq)) %>% top_n(7) %>% mutate(type = "psychic")
swatch(psychiccolors2$col_hex)
```

Rock Primary Type
```{r}
folder = "Project3/rock"
setwd(folder)
getwd()

imagesrock.png <- list.files(folder, pattern ="*.png", ignore.case = TRUE, full.names = TRUE)
imagesrock.png

rockcolors <- data.frame()

for (i in 1:length(imagesrock.png)){
    filecolorsrock <- get_colors(imagesrock.png[i], top_n = 3)
    rockcolors <- rbind(rockcolors, filecolorsrock)
}
rockcolors2 <- rockcolors %>% group_by(col_hex) %>% summarize(tot_freq = sum(col_freq)) %>% arrange(desc(tot_freq)) %>% top_n(7) %>% mutate(type = "rock")
swatch(rockcolors2$col_hex)
```

Steel Primary Type
```{r}
folder = "Project3/steel"
setwd(folder)
getwd()

imagessteel.png <- list.files(folder, pattern ="*.png", ignore.case = TRUE, full.names = TRUE)
imagessteel.png

steelcolors <- data.frame()

for (i in 1:length(imagessteel.png)){
    filecolorssteel <- get_colors(imagessteel.png[i], top_n = 3)
    steelcolors <- rbind(steelcolors, filecolorssteel)
}
steelcolors2 <- steelcolors %>% group_by(col_hex) %>% summarize(tot_freq = sum(col_freq)) %>% arrange(desc(tot_freq)) %>% top_n(7) %>% mutate(type = "steel")
swatch(steelcolors2$col_hex)
```

Water Primary Type
```{r}
folder = "Project3/water"
setwd(folder)
getwd()

imageswater.png <- list.files(folder, pattern ="*.png", ignore.case = TRUE, full.names = TRUE)
imageswater.png

watercolors <- data.frame()

for (i in 1:length(imageswater.png)){
    filecolorswater <- get_colors(imageswater.png[i], top_n = 3)
    watercolors <- rbind(watercolors, filecolorswater)
}
watercolors2 <- watercolors %>% group_by(col_hex) %>% summarize(tot_freq = sum(col_freq)) %>% arrange(desc(tot_freq)) %>% top_n(7) %>% mutate(type = "water")
swatch(watercolors2$col_hex)

# another palette view
x1 <- make_palette(watercolors, n = 7, extract_method = "hex_freq")
x2 <- head(x1, 7)
plot_colors(watercolors)

```

# all palletes in one data frame
```{r}

alltypes <-rbind(bugcolors2, darkcolors2)
alltypes <-rbind(alltypes, dragoncolors2)
alltypes <-rbind(alltypes, electriccolors2)
alltypes <-rbind(alltypes, fairycolors2)
alltypes <-rbind(alltypes, fightingcolors2)
alltypes <-rbind(alltypes, firecolors2)
alltypes <-rbind(alltypes, flyingcolors2)
alltypes <-rbind(alltypes, ghostcolors2)
alltypes <-rbind(alltypes, grasscolors2)
alltypes <-rbind(alltypes, groundcolors2)
alltypes <-rbind(alltypes, normalcolors2)
alltypes <-rbind(alltypes, poisoncolors2)
alltypes <-rbind(alltypes, psychiccolors2)
alltypes <-rbind(alltypes, rockcolors2)
alltypes <-rbind(alltypes, steelcolors2)
alltypes <-rbind(alltypes, watercolors2)
alltypes <-rbind(alltypes, icecolors2)

alltypes

write.csv(alltypes2, "colorDataPokemon.csv")
```

# Creating palette from testing subset of data
```{r}
folder = "Project3/testing"
setwd(folder)
getwd()

imagestesting.png <- list.files(folder, pattern ="*.png", ignore.case = TRUE, full.names = TRUE)
imagestesting.png

testingcolors <- data.frame()

for (i in 1:length(imagestesting.png)){
    print(imagestesting.png[i])
    filecolorstesting <- get_colors(imagestesting.png[i], top_n = 3)
    testingcolors <- rbind(testingcolors, filecolorstesting)
    #swatch(filecolors$col_hex)
}
swatch(testingcolors$col_hex)
testingcolors2 <- testingcolors %>% group_by(col_hex) %>% summarize(tot_freq = sum(col_freq)) %>% arrange(desc(tot_freq)) %>% top_n(7) %>% mutate(type = "testing")
testingcolors2
swatch(testingcolors2$col_hex)
```



-----------

# Generated top 7 colors for each pokemonin the testing data
```{r}
folder = "Project3/testing"
setwd(folder)
getwd()

imagestesting.png <- list.files(folder, pattern ="*.png", ignore.case = TRUE, full.names = TRUE)
imagestesting.png

testingcolors <- data.frame()

for (i in 1:length(imagestesting.png)){
    #print(imagestesting.png[i])
    filecolorstesting <- get_colors(imagestesting.png[i], top_n = 7) #, top_n = 1
    filecolorstestingdf <- filecolorstesting %>% mutate(name = imagestesting.png[i])
    testingcolors <- rbind(testingcolors, filecolorstestingdf)
    #swatch(filecolors$col_hex)
}

testingcolors2 <- testingcolors %>% mutate_at("name", str_replace, "Project3/testing/", "") %>% mutate_at("name", str_replace, ".png", "")

testingcolors4 <- testingcolors3
testingcolors4 <- testingcolors4[ , !names(testingcolors4) %in% remcolumns]


testingcolors2$color <- rep(1:7, length.out = 1498)
testingcolors3 <- testingcolors2 %>% pivot_wider(names_from = color, values_from =  col_hex)
testingcolors3 <- as.data.frame(testingcolors3)
remcolumns <- c("col_freq", "col_share")
testingcolors4 <- testingcolors3
testingcolors4 <- testingcolors4[ , !names(testingcolors4) %in% remcolumns]
testingcolors5 <- testingcolors4 %>% rename(hex1 = "1", hex2 = "2", hex3 = "3", hex4 = "4", hex5 = "5", hex6 = "6", hex7 = "7")
testingcolors5

testingdata <- testingcolors5 %>%
   group_by(name) %>% 
   fill(hex1, hex2, hex3, hex4, hex5, hex6, hex7) %>% 
   fill(hex1, hex2, hex3, hex4, hex5, hex6, hex7, .direction = 'up') %>%
   distinct #%>% ungroup()
testingdata

#testingcolors2 <- testingcolors2 %>% rename(tot_freq = col_freq)

write.csv(testingdata, "testingset.csv")
```

# redid training using the top 7 colors for each pokemon with their types to train model
```{r}
folder = "Project3/training"
setwd(folder)
getwd()

imagestraining.png <- list.files(folder, pattern ="*.png", ignore.case = TRUE, full.names = TRUE)
imagestraining.png

trainingcolors <- data.frame()

for (i in 1:length(imagestraining.png)){
    filecolorstraining <- get_colors(imagestraining.png[i], top_n = 7)
    filecolorstrainingdf <- filecolorstraining %>% mutate(name = imagestraining.png[i])
    trainingcolors <- rbind(trainingcolors, filecolorstrainingdf)
}
trainingcolors

trainingcolors2 <- trainingcolors %>% mutate_at("name", str_replace, "Project3/training/", "") %>% mutate_at("name", str_replace, ".png", "")

trainingcolors2 


trainingcolors4 <- trainingcolors2
trainingcolors4 <- trainingcolors4[ , !names(trainingcolors4) %in% remcolumns]

trainingcolors2$color <- rep(1:7, length.out = 3549)
trainingcolors3 <- trainingcolors2 %>% pivot_wider(names_from = color, values_from =  col_hex)
trainingcolors3 <- as.data.frame(trainingcolors3)
remcolumns <- c("col_freq", "col_share")
trainingcolors4 <- trainingcolors3
trainingcolors4 <- trainingcolors4[ , !names(trainingcolors4) %in% remcolumns]
trainingcolors5 <- trainingcolors4 %>% rename(hex1 = "1", hex2 = "2", hex3 = "3", hex4 = "4", hex5 = "5", hex6 = "6", hex7 = "7")
trainingcolors5

trainingdata <- trainingcolors5 %>%
   group_by(name) %>% 
   fill(hex1, hex2, hex3, hex4, hex5, hex6, hex7) %>% 
   fill(hex1, hex2, hex3, hex4, hex5, hex6, hex7, .direction = 'up') %>%
   distinct #%>% ungroup()
trainingdata

typedf2 <- rename(typedf2, name = Name)
typedf2

trainingdata2 <- merge(trainingdata, typedf2, by = "name")
trainingdata2

remcolumns <- c("Type2", "Evolution", "primtype")
trainingdata3 <- trainingdata2[ , !names(trainingdata2) %in% remcolumns]
trainingdata3

# removing flying type bc only 3 pokemon with primary type of flying
trainingdata3 <- trainingdata3 %>% filter(Type1 != "Flying")
trainingdata3 


write.csv(trainingdata3, "trainingset.csv")
```

